Polynomial representations of rational Cherednik algebras of type $A$ in positive characteristic $p \mid n$

### 2015-05-14 formalwriteup.tex
S_n notation, linebreak issue, shorter algebra

\author{Sheela Devadas}

@@

In this paper we study lowest-weight representations of rational Cherednik algebras associated to the symmetric group $\Sigma_n$ in characteristic $p$ dividing $n$. This problem is an interesting test case for moving results from characteristic $0$ to positive characteristic. Cherednik algebras, originally double affine Hecke algebras, were introduced by Cherednik in 1993; for an introduction to these algebras we refer to \cite{EM}. The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type $A_{n-1}$ (associated to the symmetric group $\Sigma_n$). In general new techniques are required to study positive characteristic as opposed to characteristic 0. In this paper we directly connect the characteristic 0 case for the polynomial representation to the positive characteristic case; the irreducible representation of the Cherednik algebra in this case is the quotient of the polynomial representation by an ideal generated by complex residues. In the positive characteristic case, we instead let the generators be the coefficients of formal power series. In particular our argument that this quotient is a complete intersection is directly analogous to the corresponding argument in \cite{CE}, though with additional `error terms' that emerge because we must truncate the power series so that we can define it in positive characteristic. We are able to truncate the power series because we realize the $(n-1)$-dimensional representation $\h$ of $\Sigma_n$ as a quotient by the sum of the basis elements rather than as the reflection representation.

While we only consider the case of the symmetric group $\Sigma_n$ in this paper, this technique could also be used for the general case of complex reflection groups. %this bit needs revisions

@@

Given the symmetric group $\Sigma_n$, we let $\mathcal{S}$ be the set of reflections in $\Sigma_n$. Let $\h$ be the irreducible $(n-1)$-dimensional representation of $\Sigma_n$, realized as the submodule of $k^n$ where the sum of the coordinates is $0$. For each $s \in \mathcal{S}$ we assign a vector $\alpha_s \in \h^*$ spanning the image of $1-s$, and choose $\alpha_s^\vee \in \h$ so that $(1-s)x=\langle \alpha_s^\vee,x\rangle \alpha_s$ for all $x \in \h^*$, where $\langle \cdot,\cdot\rangle$ indicates the pairing between $\h$ and $\h^*$.

Let $T(\h \oplus \h^*)$ be the tensor algebra of $\h \oplus \h^*$. We choose $\hbar,c \in k$. Then we define the {\it rational Cherednik algebra of type A $\HH_{\hbar,c}(\h)$} as the quotient of $k[\Sigma_n] \ltimes T(\h \oplus \h^*)$ by the relations
\begin{align*}
[x,x']=0, \quad [y,y' = 0], \quad [y,x] = \hbar\langle y,x\rangle - \sum_{s \in \mathcal{S}} c\langle y,\alpha_s\rangle\langle \alpha_s^\vee,x\rangle s
\end{align*}
 for all $x,x' \in \h^*, y,y' \in \h$. We can give $\HH_{\hbar,c}(\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[G]$. We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_k k[\Sigma_n] \otimes_k \Sym(\h^*)$ (\cite{EM}, section 3.2).

@@

 We call $c$ {\it generic} if we do not specify its value. We will be concerned with the case $\hbar=1$, $c$ generic, and the characteristic $p$ of $k$ dividing $n$. We realize $\h$ as the subspace of $k^n$ with the sum of the coordinates $0$, which is an irreducible representation of $\Sigma_n$ of dimension $n-1$. We state our result for this case below:

@@

To understand the action of $\HH_{\hbar,c}(\h)$ on $A$, we can use the PBW decompositions. The action of $\Sym(\h^*)$ on $A$ is by left multiplication; $k[\Sigma_n]$ acts by the diagonal action, and $\Sym(\h)$ acts via {\it Dunkl operators}. For $y \in \h$, the Dunkl operator $D_y$ acts on $A$ by:
\begin{align*}
D_y(f) = \hbar \partial_y f  - \sum_{s \in \mathcal{S}} c \frac{ ( y, \alpha_s )}{\alpha_s} (1-s). f.
\end{align*}

We choose bases for $\h,\h^*$ in the following way: let $V$ be the vector space spanned by $y_0,\dots,y_{n-1}$ and let $\h$ be the subspace spanned by $y_i-y_j$ for $i \ne j$; $\Sigma_n$ acts by permuting indices. Then if $x_0,\dots,x_{n-1}$ is the dual basis for $V^*$, we see that $\h^*$ is the span of $x_0,\dots,x_{n-1}$ under the relation $x_0+\dots+x_{n-1}=0$; alternatively we can consider $\h^*$ as the span of $x_0,\dots,x_{n-2}$ with $x_{n-1}$ defined as $-x_0-\dots-x_{n-2}$.  If $D_i$ is the Dunkl operator corresponding to $y_i$, the Dunkl operators for the elements of $\h$ are spanned by $D_i-D_j$ with $i \ne j$.

For a transposition $s_{ij} \in \Sigma_n$ with $i<j$, we let the corresponding vector $\alpha_{s_{ij}} \in \h^*$ be $x_i-x_j$.

@@

Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that $$\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z}$$ for all $0 \le i < n-1$. Let $$F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right).$$ Note that $F(z)$ is symmetric and $F_a(z)=\frac{F(z)}{1-x_az}$ for all $a$. Then we see that for all $0 \le i < n-1$ we have

\begin{align*}
\frac{\partial F}{\partial x_i}&=\frac{\partial}{\partial x_i}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial x_i}\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).\\
\end{align*}
We define $$G_i(z)=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial x_i}=G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z).$$

We can now calculate $\frac{\partial F_0}{\partial x_1},\frac{\partial F_0}{\partial x_0}$.

\begin{align*}
\frac{\partial F_0}{\partial x_1}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{1}{1-x_0z}\frac{\partial F}{\partial x_1}\\
&=\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_1(z)}{1-x_0z}\\
&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_1(z)}{1-x_0z}.\\
\end{align*}
\begin{align*}
\frac{\partial F_0}{\partial x_0}&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{z}{(1-x_0z)^2}F(z)+\frac{1}{1-x_0z}\frac{\partial F}{\partial x_0}\\
&=\frac{z}{1-x_0z}F_0(z)+\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_0(z)}{1-x_0z}\\
&=\frac{z}{1-x_0z}F_0(z)+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}\\
&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}.\\
\end{align*}

We note that $F_0(z)$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$. We see that

\begin{align*}
\frac{1-s_{0i}}{x_0-x_i}(F_0)&=\frac{1}{x_0-x_i}\left(\frac{F(z)}{1-x_0z}-\frac{F(z)}{1-x_iz}\right)\\
&=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F(z)\\
&=\frac{1}{x_0-x_i}\left(\frac{(1-x_iz)-(1-x_0z)}{(1-x_0z)(1-x_iz)}\right)F(z)\\
&=\frac{x_0z-x_iz}{(1-x_0z)(1-x_iz)(x_0-x_i)}F(z)\\
&=\frac{z}{(1-x_iz)(1-x_0z)}F(z)\\
&=\frac{z}{1-x_iz}F_0(z).\\
\end{align*}

We recall that we need only consider the action of $D_1-D_0$ on $F_0(z)$. We consider $D_0F_0, D_1F_0$ separately first. We see that $$D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)$$ since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$.

\begin{align*}
D_0F_0&=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)(F_0)\\
&=\frac{\partial F_0}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}(F_0)\\
&=\frac{G_0(z)}{1-x_0z}+\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)-\sum_{j > 0} \frac{zc}{1-x_jz}F_0(z).\\
\end{align*}
\begin{align*}
D_1F_0&=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)(F_0)\\
&=\frac{\partial F_0}{\partial x_1}+c \frac{1-s_{01}}{x_0-x_1}(F_0)\\
&=\frac{G_1(z)}{1-x_0z}+\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{zc}{1-x_1z}F_0(z)\\
&=\frac{G_1(z)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}F_0(z).\\
\end{align*}

It is then easy to see that $$(D_1-D_0)(F_0)=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0.$$

@@

We see easily that $$\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.$$ We now consider $\frac{\partial F}{\partial z}$.

\begin{align*}
\frac{\partial F}{\partial z}&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
\end{align*}
We define $$V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).$$

From this it follows that

\begin{align*}
\frac{\partial F_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_0z}\right)\\
&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F(z)\\
&=\frac{V(z)}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_0}{(1-x_0z)^2} F(z)\\
&=\frac{V(z)}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0(z)+\frac{x_0}{1-x_0z} F_0(z).\\
\end{align*}

We now again consider $(D_1-D_0)(F_0)$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $F_0$ since that is $0$ in characteristic $p$.

>>>>

\author{Sheela Devadas and Yi Sun}

@@

In this paper we study lowest-weight representations of rational Cherednik algebras associated to the symmetric group $S_n$ in characteristic $p$ dividing $n$. This problem is an interesting test case for moving results from characteristic $0$ to positive characteristic. Cherednik algebras, originally double affine Hecke algebras, were introduced by Cherednik in 1993; for an introduction to these algebras we refer to \cite{EM}. The representation theory of these algebras has been studied more extensively in characteristic $0$ than in positive characteristic, including the case of Cherednik algebras of type $A_{n-1}$ (associated to the symmetric group $S_n$). In general new techniques are required to study positive characteristic as opposed to characteristic 0. In this paper we directly connect the characteristic 0 case for the polynomial representation to the positive characteristic case; the irreducible representation of the Cherednik algebra in this case is the quotient of the polynomial representation by an ideal generated by complex residues. In the positive characteristic case, we instead let the generators be the coefficients of formal power series. In particular our argument that this quotient is a complete intersection is directly analogous to the corresponding argument in \cite{CE}, though with additional `error terms' that emerge because we must truncate the power series so that we can define it in positive characteristic. We are able to truncate the power series because we realize the $(n-1)$-dimensional representation $\h$ of $S_n$ as a quotient by the sum of the basis elements rather than as the reflection representation.

While we only consider the case of the symmetric group $S_n$ in this paper, this technique could also be used for the general case of complex reflection groups. %this bit needs revisions

@@

Given the symmetric group $S_n$, we let $\mathcal{S}$ be the set of reflections in $S_n$. Let $\h$ be the irreducible $(n-1)$-dimensional representation of $S_n$, realized as the submodule of $k^n$ where the sum of the coordinates is $0$. For each $s \in \mathcal{S}$ we assign a vector $\alpha_s \in \h^*$ spanning the image of $1-s$, and choose $\alpha_s^\vee \in \h$ so that $(1-s)x=\langle \alpha_s^\vee,x\rangle \alpha_s$ for all $x \in \h^*$, where $\langle \cdot,\cdot\rangle$ indicates the pairing between $\h$ and $\h^*$.

Let $T(\h \oplus \h^*)$ be the tensor algebra of $\h \oplus \h^*$. We choose $\hbar,c \in k$. Then we define the {\it rational Cherednik algebra of type A $\HH_{\hbar,c}(\h)$} as the quotient of $k[S_n] \ltimes T(\h \oplus \h^*)$ by the relations
\begin{align*}
[x,x']=0, \quad [y,y' = 0], \quad [y,x] = \hbar\langle y,x\rangle - \sum_{s \in \mathcal{S}} c\langle y,\alpha_s\rangle\langle \alpha_s^\vee,x\rangle s
\end{align*}
 for all $x,x' \in \h^*, y,y' \in \h$. We can give $\HH_{\hbar,c}(\h)$ a $\mathbb{Z}$-grading by setting $\deg x=1$ for $x \in \h^*$, $\deg y = -1$ for $y \in \h$, and $\deg g=0$ for $g \in k[G]$. We get the PBW-type decomposition $\HH_{\hbar,c}(\h)=\Sym(\h) \otimes_k k[S_n] \otimes_k \Sym(\h^*)$ (\cite{EM}, section 3.2).

@@

 We call $c$ {\it generic} if we do not specify its value. We will be concerned with the case $\hbar=1$, $c$ generic, and the characteristic $p$ of $k$ dividing $n$. We realize $\h$ as the subspace of $k^n$ with the sum of the coordinates $0$, which is an irreducible representation of $S_n$ of dimension $n-1$. We state our result for this case below:

@@

To understand the action of $\HH_{\hbar,c}(\h)$ on $A$, we can use the PBW decompositions. The action of $\Sym(\h^*)$ on $A$ is by left multiplication; $k[S_n]$ acts by the diagonal action, and $\Sym(\h)$ acts via {\it Dunkl operators}. For $y \in \h$, the Dunkl operator $D_y$ acts on $A$ by:
\begin{align*}
D_y(f) = \hbar \partial_y f  - \sum_{s \in \mathcal{S}} c \frac{ ( y, \alpha_s )}{\alpha_s} (1-s). f.
\end{align*}

We choose bases for $\h,\h^*$ in the following way: let $V$ be the vector space spanned by $y_0,\dots,y_{n-1}$ and let $\h$ be the subspace spanned by $y_i-y_j$ for $i \ne j$; $S_n$ acts by permuting indices. Then if $x_0,\dots,x_{n-1}$ is the dual basis for $V^*$, we see that $\h^*$ is the span of $x_0,\dots,x_{n-1}$ under the relation $x_0+\dots+x_{n-1}=0$; alternatively we can consider $\h^*$ as the span of $x_0,\dots,x_{n-2}$ with $x_{n-1}$ defined as $-x_0-\dots-x_{n-2}$.  If $D_i$ is the Dunkl operator corresponding to $y_i$, the Dunkl operators for the elements of $\h$ are spanned by $D_i-D_j$ with $i \ne j$.

For a transposition $s_{ij} \in S_n$ with $i<j$, we let the corresponding vector $\alpha_{s_{ij}} \in \h^*$ be $x_i-x_j$.

@@

Since $x_{n-1}=-x_0-\dots-x_{n-2}$, we see that $$\frac{\partial g}{\partial x_i}=-\frac{zg}{1-x_iz}+\frac{zg}{1-x_{n-1}z}$$ for all $0 \le i < n-1$. Let $$F(z) =\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right).$$ Note that $F(z)$ is symmetric and $F_a(z)=\frac{F(z)}{1-x_az}$ for all $a$. Then we see that for all $0 \le i < n-1$ we have 
\begin{align*}
\frac{\partial F}{\partial x_i}%&=\frac{\partial}{\partial x_i}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial x_i}\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g\\
%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g\\
%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
%&=\left(-\frac{z}{1-x_iz}+\frac{z}{1-x_{n-1}z}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}+F(z)\right).\\
\end{align*}
We define $$G_i(z)=\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)\left(-\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial x_i}=G_i(z)+\left(-\frac{zc}{1-x_iz}+\frac{zc}{1-x_{n-1}z}\right)F(z).$$

We can now calculate $\frac{\partial F_0}{\partial x_1},\frac{\partial F_0}{\partial x_0}$. 
\begin{align*}
\frac{\partial F_0}{\partial x_1}%&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{1}{1-x_0z}\frac{\partial F}{\partial x_1}\\
&=\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_1(z)}{1-x_0z}\\
&=\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_1(z)}{1-x_0z}.\\
\frac{\partial F_0}{\partial x_0}%&=\frac{\partial}{\partial x_1}\left(\frac{1}{1-x_0z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\right)\\
&=\frac{z}{(1-x_0z)^2}F(z)+\frac{1}{1-x_0z}\frac{\partial F}{\partial x_0}\\
&=\frac{z}{1-x_0z}F_0(z)+\frac{1}{1-x_0z}\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F(z)+\frac{G_0(z)}{1-x_0z}\\
%&=\frac{z}{1-x_0z}F_0(z)+\left(-\frac{zc}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}\\
&=\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{G_0(z)}{1-x_0z}.\\
\end{align*}
We note that $F_0(z)$ is invariant under $s_{ij}$ where $0 < i,j$. Therefore for transpositions we need only consider transpositions of the form $s_{0i}$ for $0 < i \le n-1$. We see that 
\begin{align*}
\frac{1-s_{0i}}{x_0-x_i}(F_0)%&=\frac{1}{x_0-x_i}\left(\frac{F(z)}{1-x_0z}-\frac{F(z)}{1-x_iz}\right)\\
&=\frac{1}{x_0-x_i}\left(\frac{1}{1-x_0z}-\frac{1}{1-x_iz}\right)F(z)\\
%&=\frac{1}{x_0-x_i}\left(\frac{(1-x_iz)-(1-x_0z)}{(1-x_0z)(1-x_iz)}\right)F(z)\\
%&=\frac{x_0z-x_iz}{(1-x_0z)(1-x_iz)(x_0-x_i)}F(z)\\
&=\frac{z}{(1-x_iz)(1-x_0z)}F(z)\\
&=\frac{z}{1-x_iz}F_0(z).\\
\end{align*}
We recall that we need only consider the action of $D_1-D_0$ on $F_0(z)$. We consider $D_0F_0, D_1F_0$ separately first. We see that $$D_0=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right), D_1=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)$$ since $F_0$ is invariant under $s_{ij}$ where $0 < i,j$. 
\begin{align*}
D_0F_0&=\left(\frac{\partial}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}\right)(F_0)\\
&=\frac{\partial F_0}{\partial x_0}-c\sum_{j > 0} \frac{1-s_{0j}}{x_0-x_j}(F_0)\\
&=\frac{G_0(z)}{1-x_0z}+\left(\frac{z(1-c)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)-\sum_{j > 0} \frac{zc}{1-x_jz}F_0(z).\\
D_1F_0&=\left(\frac{\partial}{\partial x_1}-c \frac{1-s_{01}}{x_1-x_0}\right)(F_0)\\
&=\frac{\partial F_0}{\partial x_1}+c \frac{1-s_{01}}{x_0-x_1}(F_0)\\
&=\frac{G_1(z)}{1-x_0z}+\left(-\frac{zc}{1-x_1z}+\frac{zc}{1-x_{n-1}z}\right)F_0(z)+\frac{zc}{1-x_1z}F_0(z)\\
&=\frac{G_1(z)}{1-x_0z}+\frac{zc}{1-x_{n-1}z}F_0(z).\\
\end{align*}
It is then easy to see that $$(D_1-D_0)(F_0)=\frac{G_1-G_0}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0.$$

@@

We see easily that $$\frac{\partial g}{\partial z} = g(z) \sum_j \frac{-x_j}{1-x_jz}.$$ We now consider $\frac{\partial F}{\partial z}$.
\begin{align*}
\frac{\partial F}{\partial z}%&=\frac{\partial}{\partial z}\left(\sum_{k=0}^{p-1} \binom{c}{k} (g-1)^k\right)\\
&=\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)\frac{\partial g}{\partial z}\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=1}^{p-1}k\binom{c}{k}(g-1)^{k-1}\right)g(z)\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}(k+1)\binom{c}{k+1}(g-1)^{k}\right)g(z)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)(g-1+1)\\
%&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k+1}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(\left(\sum_{k=0}^{p-2}c\binom{c-1}{k}(g-1)^{k}\right)+\left(\sum_{k=1}^{p-1}c\binom{c-1}{k-1}(g-1)^{k}\right)\right)\\
&=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}+\sum_{k=0}^{p-1}c\binom{c}{k}(g-1)^{k}\right)\\
&=\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).
\end{align*}
We define $$V(z)=\left(\sum_j \frac{-x_j}{1-x_jz}\right)\left(-c\binom{c-1}{p-1}(g-1)^{p-1}\right).$$ Then we see that $$\frac{\partial F}{\partial z}=V(z)+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z).$$

From this it follows that
\begin{align*}
\frac{\partial F_0}{\partial z} &= \frac{\partial}{\partial z}\left(\frac{F(z)}{1-x_0z}\right)\\
&=\frac{1}{1-x_0z} \frac{\partial F}{\partial z}+\frac{x_0}{1-x_0z} F(z)\\
&=\frac{V(z)}{1-x_0z}+\frac{1}{1-x_0z}\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F(z)+\frac{x_0}{(1-x_0z)^2} F(z)\\
&=\frac{V(z)}{1-x_0z}+\left(\sum_j \frac{-cx_j}{1-x_jz}\right)F_0(z)+\frac{x_0}{1-x_0z} F_0(z).\\
\end{align*}
We now again consider $(D_1-D_0)(F_0)$. Recall that $n \equiv 0 \bmod p$, so in particular we can add $n$ times any multiple of $F_0$ since that is $0$ in characteristic $p$. 
\begin{align*}
(D_1-D_0)(F_0)&=\frac{G_1(z)-G_0(z)}{1-x_0z}+\frac{z(c-1)}{1-x_0z}F_0+\sum_{j>0} \frac{zc}{1-x_jz}F_0\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\sum_{j} \frac{zc}{1-x_jz}F_0\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{zc}{1-x_jz}F_0\right)-nzcF_0\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+zF_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} -zcF_0+\frac{zc}{1-x_jz}F_0\right)\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{z-x_0z^2}{1-x_0z}F_0-\frac{z}{1-x_0z}F_0+\left(\sum_{j} \frac{-zc+x_jcz^2}{1-x_jz}F_0+\frac{zc}{1-x_jz}F_0\right)\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0+\frac{-x_0z^2}{1-x_0z}F_0+\left(\sum_{j} \frac{x_jcz^2}{1-x_jz}F_0\right)\\
%&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\left(\frac{x_0}{1-x_0z}F_0+\left(\sum_{j}- \frac{x_jc}{1-x_jz}F_0\right)\right)\\
&=\frac{G_1(z)-G_0(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}+z^2\frac{V(z)}{1-x_0z}\\
&=\frac{G_1(z)-G_0(z)+z^2V(z)}{1-x_0z}-zF_0-z^2\frac{\partial F_0}{\partial z}.\\
\end{align*}
We consider $z^2V(z)$ and $G_i(z)$ for $i=0,1$. We note that $(g-1)^{p-1}$ divides $V(z)$ and $z(g-1)^{p-1}$ divides $G_i(z)$. Since the sum $\sum_{a=0}^{n-1} x_a$ is $0$, we see that $z^2 \mid g(z)-1$; therefore $z^{2p-2} \mid (g-1)^{p-1}$. Therefore $z^{p+1} \mid z^{2p-1} \mid G_i(z)$ and $z^{p+1} \mid z^{2p} \mid z^2V(z)$. (We note that $z^p \mid z^{2p-2} \mid V(z)$; this will be relevant later.)
